A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
fpp text changes; some quant added

A major problem with any transit search is the potential confusion
between transiting planets and stellar eclipsing binaries.  Of
particular concern are grazing stellar eclipses or stellar eclipses
that contribute only a small fraction of the total light in a
photometric aperture, resulting in greatly diluted eclipse depths able
to mimic the signals of small planets.

@@

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to two major factors.  First, the superior precision of
the \kepler\ photometry enables detection of secondary stellar
eclipses to a much lower level than ground-based surveys; and second,
the relatively small pixels and stable pointing of the
\kepler\ telescope has enabled the identification of many spatially
distinct blended eclipsing binaries by means of detailed pixel-level
analysis \citep{Bryson:2013}.

Ground-based surveys prior to \kepler\ often had a false-positive rate
of 30 to 40~percent. \dfmtodo{(because of shit?) Because of giant pixels.
See references in Morton and Johnson intro, probably}
In the primary \kepler\ Mission, this number was significantly lower:
the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of the \kepler\ spacecraft.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
variations between transits \dfmtodo{(e.g. citation)}.

@@

To obtain an initial assessment of the astrophysical false positive rate in
our catalog of planet candidates, we test for significant centroid offsets
using the machinery that we have already established for modeling the
systematic trends in the data.
This is only the first word and a more complete characterization of our
catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in
preparation).

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (Vakili \etal, in preparation).
\Fig{centroid} shows the measured $x$ and $y$ pixel coordinate traces for EPIC
201613023.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (\eqalt{linear-model}), we modeled the light curve as a linear
combination of ELCs and a simple box transit model at a given period, phase,
and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
than the random realizations, we label the candidate as a false positive.
In practice, the precision of the centroid measurements isn't sufficient to
robustly reject many candidates but two candidates---EPIC 201202105 and EPIC
201632708---have offsets large enough that we remove them from our final
catalog.

>>>>

A major problem with any transit search is the potential confusion
between transiting planets and stellar eclipsing binaries (EBs).  Of
particular concern are grazing stellar eclipses or stellar eclipses
that contribute only a small fraction of the total light in a
photometric aperture, resulting in greatly diluted eclipse depths able
to mimic the signals of small planets.

@@

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to three major factors.  First, the superior precision
of the \kepler\ photometry enables detection of secondary stellar
eclipses, odd-even transit depth variations, and ellipsoidal
variations \citep{Batalha:2010} to a much lower level than
ground-based surveys. Second, the relatively small pixels and stable
pointing of the \kepler\ telescope has enabled the identification of
many spatially distinct blended eclipsing binaries by means of
detailed pixel-level analysis \citep{Bryson:2013} to identify shifts
in the center of light during transits.  And finally, \kepler\ is
sensitive to much smaller planets than ground-based surveys, and it
turns out that small planets are much more common than hot Jupiters.

@@

To do first-pass vetting for blended EBs among our catalog of
planetary candidates, we test for significant centroid offsets using
the machinery that we have already established for modeling the
systematic trends in the data, inspired by the methods used to vet
\kepler\ candidates \citep{Bryson:2013}.  This is only an initial vetting step
and a more complete characterization of our catalog's reliability is
forthcoming (Montet, Foreman-Mackey, \etal\ in preparation).

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (Vakili \etal, in preparation).
\Fig{centroid} shows the measured $x$ and $y$ pixel coordinate traces for EPIC
201613023.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (\eqalt{linear-model}), we modeled the light curve as a linear
combination of ELCs and a simple box transit model at a given period, phase,
and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
than the random realizations, we label the candidate as a false positive.
In practice, the precision of the centroid measurements isn't sufficient to
robustly reject many candidates, but two candidates---EPIC 201202105 and EPIC
201632708---have offsets large enough that we remove them from our final
catalog.

A quick \emph{a priori} estimate of the background blended ecipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that something close to
$\sim$10\% of stars might host close binary companions within the
period range accessible by this survey, this gives a probability of
0.016 that a blended binary star might be chance-aligned within two
pixels of any given target star.  Noting that the average number of
planets per star with periods less than 30 days is about 0.25
\citep{Fressin:2013}, we can roughly estimate that we expect $<$10\%
of our candidates to be caused by nearby contaminating EBs.  This
estimate suggests that such astrophsycial false positives should be
rare in our sample, consistent with our detection of 2/36 candidates
with clear centroid offsets.
